### 2021-04-08 papers/SYRCoSE/intro.tex
Introduction: typos, grammar, wording

The main advantage of the event structures 
compared to traditional interleaving semantics 
is that they give a more compact and concise 
representation of programs' behaviour.
For example, consider the following code snippet.

@@

Under the interleaving semantics 
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted on \cref{fig:intro-traces}.
Event themselves represent atomic side-effects produced by the execution of instruction. 
In our case it is either a write of a value to a shared variable $\wlab{x}{a}$,
or a read of a particular value from a shared variable $\rlab{x}{a}$.

@@

In the programming language and formal semantics research communities 
it becomes the de-facto standard to complement the theoretical 
studies with their mechanisation in the \emph{proof assistants}
like Coq, Agda, Isabelle, Arend, and others,
as this process increases the reliability and reproducibility 
of the scientific results.
Yet, as far as we know, there is a little work on 
mechanisation of event structures theory.

Our work is aimed to close this gap. 
Our goal is to develop a Coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow the researchers 
to utilise the theory of event structures 
for the needs of their domain.

>>>>

The main advantage of event structures
compared to traditional interleaving semantics 
is that they give a more compact and concise 
representation of programs' behaviours.
For example, consider the following code snippet
of a simple parallel program.

@@

Under the interleaving semantics 
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted in \cref{fig:intro-traces}.
Events themselves represent atomic side-effects produced by instruction executions.
In our case an event is either a \emph{write} of a value $a$ to a shared variable $x$ denoted as $\wlab{x}{a}$,
or a \emph{read} of a value $a$ from a shared variable $x$ denoted as $\rlab{x}{a}$.

@@

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like Coq, Agda, Isabelle, Arend, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

Our goal is to develop a Coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.
